---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)

Title <- "TODO"
Authors <- "Andrew Heiss and Meng Ye"
Year <- "2023"
```

# `r Title`

[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
Meng Ye • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

TODO

---

## `r emoji::emoji_glue(":blueberries::monkey:")`: "Mulberry monkey" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.5.0. R version 4.3.1 (2023-06-16).

codename(seed = "ta ongo china", type = "ubuntu")
#> [1] "mulberry monkey"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
